TacticToe: Learning to Prove with Tactics

### 2018-08-20 tactictoe_jv.tex
draft: proof planning related work

A closely related approach is proof planning that was firstly describe in 
~\cite{}. Proof planning is a meta approach to tactics constructing more and 
more general tactics by sharing common proof patterns between different tactics.
Comparatively, our approach tries to automate the construction of proof plans 
by letting MCTS policy decide which tactics is the best in each situation. Our 
approach can be thought as one general proof plan only guided by previous human 
proofs. 
From another angle, if we think of proof plans as ``domain'' specific tactics 
our approach does not try to synthetize proof plan automatically but just 
re-use them if they already exists.

>>>>

A closely related approach is proof planning that was firstly describe in 
~\cite{proofplan}. ~\cite{oyster}
The philosophy of proof planning is to create (automatically or not) a few 
tactics can prove a wide range of theorems. In this respect, if you consider 
MCTS to be a proof plan then we have produced one general tactic that learns 
from examples and has a large success rate.
But proof planning is also concerned with tactic synthesis where new proof 
plans (tactics in \holfour) may be discovered automatically from examples.
From this point of view, \tactictoe does not look at proof patterns to infer 
new tactics and creates new tactics only by abstracting arguments. Therefore, 
it would be interesting to see how including tactic synthesis or even 
human-designed proof plans (such as rippling~\cite{rippling}) in the database 
of tactics $\mathbb{D}_{\mathit{tactic}}$.
Proof planning is a meta approach to tactics constructing more and 
more general tactics by sharing common proof patterns between different tactics.
Comparatively, our approach tries to automate the construction of proof plans 
by letting MCTS policy decide which tactics is the best in each situation. Our 
approach can be thought as one general proof plan only guided by previous human 
proofs. 
From another angle, if we think of proof plans as clever more general specific 
tactics (like inductionless induction\cite{})
our approach does not try to synthetize proof plan automatically but just 
re-use them if they already exists.
